Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-22 manuscript/climate_sensitivity_draft.Rmd
word count and word version for coauthors

Text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) | 6,603 **(Limit 6500)**	 |	No. of figures | 	4 (all colour)
Summary|  	200 | 	No. of Tables | 	3  
Introduction|	1,264 |	No of Supporting Information files | 	19
Materials and Methods |	2,178	||	 
Results |	1126	 ||
Discussion |	1953	||
Acknowledgments | 142	||

>>>>

Text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) | 6,458 **(Limit 6500)**	 |	No. of figures | 	4 (all colour)
Summary|  	200 | 	No. of Tables | 	3  
Introduction|	1,340 |	No of Supporting Information files | 	19
Materials and Methods |	2,036	||	 
Results |	1124	 ||
Discussion |	1952	||
Acknowledgments | 142	||
